---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Load the librarys for this procject
```{r}
library('ggplot2')
library(lattice)

```
## Loading and preprocessing the data
Load the csv
```{r}
activity = read.csv('activity.csv', header = T)
activity$date <- as.Date(activity$date, format="%Y-%m-%d")
activity.stepperday = aggregate(steps ~ date, activity, FUN=sum,na.rm=TRUE)
colnames(activity.stepperday) <- c("Date", "Steps")
ggplot(activity.stepperday, aes(x=Steps)) + 
geom_histogram(fill="steelblue", binwidth=800) + 
labs(title="Histogram of Steps Taken per Day", x="Number of Steps", y="Count") + 
theme_bw() + theme(legend.position = "bottom")    
```

## What is mean total number of steps taken per day?
```{r}
mean(activity.stepperday$Steps)
```

## What is median total number of steps taken per day?
```{r}
median(activity.stepperday$Steps)
```

## What is the average daily activity pattern?
```{r}
activity.stepsinterval<-aggregate(steps~interval,data=activity,mean,na.rm=TRUE)
colnames(activity.stepsinterval) <- c("Interval", "Steps")
j <- activity.stepsinterval[which.max(activity.stepsinterval$Steps),]$Interval
ggplot(data=activity.stepsinterval, aes(x=Interval, y=Steps)) + geom_line() +
    geom_point() + geom_hline(aes(yintercept=round(max(Steps),1)),color="steelblue") + geom_text(aes( 300, max(Steps), label = paste("Maximum number of steps: ", round(max(Steps),1)), vjust = -1), size = 3,color="steelblue") + geom_vline(xintercept=j,color="green") + 
    geom_text(aes( j+150, 10, label = paste("Interval: ", j)), size = 3,color="green")+ 
theme_bw()    
```

## Number of rows with NA's
```{r}
sum(is.na(activity$steps))

```

## Replacing the NA's with the mean 
```{r}
teactivity <- activity
teactivity[is.na(teactivity)] <- mean(teactivity$steps, na.rm=T)
activity.stepperdaynna = aggregate(steps ~ date, teactivity, FUN=sum,na.rm=TRUE)

ggplot(activity.stepperdaynna, aes(x=steps)) + 
geom_histogram(fill="steelblue", binwidth=800) + 
labs(title="Histogram of Steps Taken per Day Replacing NA with mean", x="Number of Steps", y="Count") + 
theme_bw() + theme(legend.position = "bottom")    
```

### Mean of steps with replaced NA's
```{r}
mean(activity.stepperdaynna$steps)
```

### Median of steps with replaced NA's
```{r}
median(activity.stepperdaynna$steps)
```

### After replacing the mean is equal to the median
```{r}
mean(activity.stepperdaynna$steps) - median(activity.stepperdaynna$steps)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
teactivity$day = ifelse(as.POSIXlt(teactivity$date)$wday%%6 == 
    0, "weekend", "weekday")
teactivity$day = factor(teactivity$day, levels = c("weekday", "weekend"))
activity.stepperdaycompa = aggregate(steps ~ interval + day, teactivity, mean)
xyplot(steps ~ interval | factor(day), data = activity.stepperdaycompa, aspect = 1/2, 
    type = "l")
```

